The Cost of Transportation : Spatial Analysis of US Fuel Prices

### 2017-07-24 Docs/arxiv/v1/paper.tex
resp_rev

There exists to our knowledge no systematic mapping in space and time of retail fuel prices for a large country such as the US. The main reason is probably that the availability of data have been a significant obstacle. It is also likely that the nature of the problem may also have influence, as it lies at the crossroad of several disciplines. While economists study price elasticity and measurement in different markets, transportation geography with methods such as transportation prices in spatial models, puts more emphasis on spatial distribution than on precise market mechanisms. Nevertheless, examples of somehow related works can be found. For example,~\cite{rietveld2001spatial} studies the impact of cross-border differences in fuel price and the implications for gradual spatial taxation in Netherlands. At the country-level, \cite{rietveld2005fuel} provides statistical models to explain fuel price variability across European countries. \cite{macharis2010decision} models the impact of spatial fuel price variation on patterns of inter-modality, implying that the spatial heterogeneity of fuel prices has a strong impact on user behavior. With a similar view on the geography of transportation, \cite{gregg2009temporal} studies spatial distribution of gas emission at the US-state level. The geography of fuel prices also have important implications on effective costs, as shows \cite{combes2005transport} by determining accurate transportation costs across urban areas for France. More closely related to our work, and using very similar daily open data for France, \cite{gautier2015dynamics} investigate dynamics of transmission from crude oil prices to fuel retail prices. However, they do not introduce an explicit spatial model of prices diffusion and do not study spatio-temporal dynamics. \cite{deltas2008retail} studies a long-time panel of prices in the US to show an asymmetry in response to wholesale price variations, but stays at the State level. A review on empirical studies of gasoline retailing done by~\cite{eckert2013empirical} confirms that station-level studies are few and imply small countries only such as Belgium or Austria, or single US States.

In this paper we adopt a broader approach by proceeding to exploratory spatial analysis on fuel prices for the whole US. We show that most of the variation occurs between counties and not across time, although crude oil price was not constant during the period considered. We therefore turn to a spatial analysis of the distribution of fuel prices. Our main findings are twofold: first we show that there are significant spatial pattern in some large US regions, second we show that even if most of the observed variation can be explained by state level policies, and especially the level of tax, some county level characteristics are still significant.

@@

The availability of new type of data has induced consequent changes in various disciplines from social science (e.g. online social network analysis~(\cite{tan2013social})) to geography (e.g. new insights into urban mobility or perspectives on ``smarter'' cities~(\cite{batty2013big})) including economics where the availability of exhaustive individual or firm level data is seen as a revolution of the field. Most studies involving these new data are at the interface of implied disciplines, what is both an advantage but also a source of difficulties. % For example misunderstandings between physics and urban sciences described in \cite{dupuy2015sciences} are in particular caused by different attitudes towards unconventional data or divergent interpretations and ontologies of it.
 Collection and use of new data has therefore become a crucial stack in social-science. The construction of such datasets is however far from straightforward because of the incomplete and noisy nature of data. Specific technical tools have to be implemented but have often been designed to overcome one specific problem and are difficult to generalize. We develop such a tool that fills the following constraints that are typical of large scale data collection, namely a reasonable level of flexibility and generality, an optimized performance through parallel collection jobs, and the anonymity of collection jobs to avoid any possible bias in the behavior of the data source. The architecture, at a high level, has the following structure: (i) an independent pool of tasks runs continuously socket proxies to pipe requests through \texttt{tor}; (ii) a manager monitors current collection tasks, split collection between subtasks and launches new ones when necessary; (iii) Subtasks can be any callable application taken as argument destination urls, they proceed to the crawling, parsing and storage of collected data. The application is open and its modules are reusable: source code is available on the repository of the project.\footnote{at \texttt{https://github.com/JusteRaimbault/EnergyPrice}} We constructed our dataset by using the tool continuously in time during two months to collect crowdsourced data available from various online sources.

@@

Our dataset comprises around $41\cdot 10^6$ unique observations of retail fuel prices at the station level, spanning the period starting the $10^{th}$ of January 2017 and ending the $19^{th}$ of March 2017 and corresponds to 118,573 unique retail stations. For each of these stations, we associate a precise geographical location (city resolution). On average we have 377 price informations by station. Prices correspond to a unique purchase mode (credit card, other modes such as cash being less than 10\% in test datasets, they were discarded in the final dataset) and four possible fuel types: Diesel (18\% of observations), Regular (34\%), Midgrade (24\%) and Premium (24\%). The best coverage of stations is for Regular fuel type with on average 4,629 price information by county. We therefore choose to focus the study to this type of fuel, keeping in mind that further developments with the dataset may include comparative analysis on fuel types.
Our final dataset thus contains 14,192,352 observations from 117,155 gas stations, followed during 68 days. We further aggregate these data by day, taking the average of the observed price per gallon, to obtain a panel of 5,204,398 gas station - day observations.\footnote{The panel is not balanced as prices are not reported every day in every station. The average gas station has information on price for 44 days (over 68).}  Table \ref{tab:stat_desc} gives some basic descriptive statistics of on price data showing that the distribution of oil price is highly concentrated with a small skewness (the ratio of the $99^{th}$ to the $1^{st}$ percentile is 1.6). 
Finally, in the spatial analysis, we will also use socio-economic data at the county level, available from the US Census Bureau. We shall use the latest available, what most of the time implies relying to the 2010 Census.

@@

Before moving to a more systematic study of the variation of fuel price, we propose a first exploratory introduction to give insight about its spatio-temporal structure. This exercise is a crucial stage to guide further analyses, but also to understand their implications in a geographical context. To explore the data, we built a simple web application which allow to map the data in space and time. This application is available on \href{http://shiny.parisgeo.cnrs.fr/fuelprice}{this page}. We also show one example of mapping the data at the county level in Figure \ref{fig:map_price} where we used average price over the whole period. We clearly see regional patterns with the Southcentral and Southeast regions having the lowest prices and the Pacific cost and Northeast the highest prices. Of course, plotting aggregated data over the whole period does not bring much information about the time variation of the data. As we will show more in detail below most of the variation of fuel price occurs across space. A variance decomposition of fuel price yields only 11\% of the total variance is explained by within gas station variations. Similarly, the Spearman's rank correlation coefficient between the gas station price of regular fuel in the first day of dataset and in the last day is 0.867, and the null hypothesis that these two information are independent is strongly rejected.

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/average_regular_map}
\caption{Map of mean price for counties, regular fuel, averaged over the whole period.}\vspace{-0.3cm}
\label{fig:map_price}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{figures/moran_days}
\includegraphics[width=0.48\textwidth]{figures/moran_decay_weeks}
\caption{\textbf{Behavior of Moran spatial-autocorrelation index.} (Left) Evolution in time of Moran index computed on daily time windows, for different decay parameter values. (Right) Moran index as a function of decay parameter, computed on weekly time windows.}
\label{fig:moran}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{figures/gwr_allbest_betaincome}
\includegraphics[width=0.48\textwidth]{figures/gwr_allbest_betapercapjobs}\\
%\includegraphics[width=0.48\textwidth]{figures/gwr_allbest_residual}
\includegraphics[width=0.48\textwidth]{figures/gwr_allbest_wage}
\includegraphics[width=0.48\textwidth]{figures/gwr_allbest_LocalR2}
\caption{\textbf{Results of GWR analyses.} For the best model in the sense of AICc, we map the spatial distribution of fitted coefficient, in order from left to right and top to bottom, $\beta_{income}$, $\beta_{percapjobs}$, $\beta_{wage}$, and finally the local r-squared values.}
\label{fig:gwr}
\end{figure}

@@

Since our initial database enables to look at the level of variable $x_{i,s,c,t}$, the fuel price in day $t$, in gas station $i$, in state $s$ and in county $c$, we start by running high dimensional fixed effect regressions following the model:
\begin{eqnarray}
x_{i,s,c,t} &=& \beta_s + \varepsilon_{i,s,c,t} \\
x_{i,s,c,t} &=& \beta_c + \varepsilon_{i,s,c,t} \\
x_{i,s,c,t} &=& \beta_i + \varepsilon_{i,s,c,t}
\end{eqnarray}

where $\varepsilon_{i,s,c,t}$ contains an idiosyncratic error and a day fixed effect. This first analysis confirm that most of the variance can be explained by a state fixed effect and that integrating more accurate levels has only small effect on the fit of our model as measured by the R-squared.

@@

One important aspect of our contribution is methodological. We show that to explore a new panel dataset, geographers and economists have different approaches, leading to similar generic conclusions but with different paths. Some studies have already combined GWR and multi-level regressions (\cite{chen2012using}), or compared them in terms of model fit or robustness (\cite{lee2009determinants}). We take here a multi-disciplinary point of view and combine approaches answering to different questions, GWR aiming at finding precise explicative variables and to measure the extent of spatial correlation, whereas econometric models explain with more accuracy the effect of factors at different levels (state, county) but take these geographical characteristics as exogenous. We claim that both are necessary to understand all dimensions of the studied phenomenon.

@@

Another potential application of our analysis is to help better designing car-regulation policies. Environmental and health issues nowadays require a reasoned use of cars, in cities with the problem of air pollution but also overall to reduce carbon emissions. \cite{fullerton2002can} showed that a taxation of fuel and cars can be equivalent to a taxation on emissions. \cite{brand2013accelerating} highlight the role of incentives for the transition towards a low carbon transportation. However, such measures can't be uniform across states or even counties for obvious reasons of territorial equity: areas with different socio-economic characteristics or with different amenities shall contribute regarding their capabilities and preferences. Knowing local prices dynamics and their drivers, in which our study is a preliminary step, may be a path to localized policies taking into account the socio-economic configuration and include an equity criterion.

@@

We have described a first exploratory study of US fuel prices in space and time, using a new database at the gas station level spanning two months. Our first result is to show the high spatial heterogeneity of price processes, using interactive data exploration and auto-correlation analyses. We proceed with two complementary studies of potential drivers: GWR unveils spatial structures and geographical particularities, and yields a characteristic scale of processes around 75km; multi-level regressions show that even though most of the variation can be explained by state level characteristics, and mostly by the level of the tax on fuel that is set by the state, there are still socio-economic specificities at the county level that can explain spatial variation of fuel price. Our contribution paves the way for further detailed studies using similar micro-level datasets.

@@

%The citation must be used in following style: \cite{article-minimal} \cite{article-full} \cite{article-crossref} \cite{whole-journal}.
%% References with BibTeX database:

\bibliographystyle{elsarticle-harv}
\bibliography{biblio}
%

>>>>

There exists to our knowledge no systematic mapping in space and time of retail fuel prices for a country. The main reason is probably that the availability of data have been a significant obstacle. It is also likely that the nature of the problem may also have influence, as it lies at the crossroad of several disciplines. While economists study price elasticity and measurement in different markets, transportation geography with method such as transportation prices in spatial models, puts more emphasis on spatial distribution than on precise market mechanisms. Nevertheless, examples of somehow related works can be found. For example,~\cite{rietveld2001spatial} studies the impact of cross-border differences in fuel price and the implications for gradual spatial taxation in Netherlands. At the country-level, \cite{rietveld2005fuel} provides statistical models to explain fuel price variability across European countries. \cite{macharis2010decision} models the impact of spatial fuel price variation on patterns of inter-modality, implying that the spatial heterogeneity of fuel prices has a strong impact on user behavior. With a similar view on the geography of transportation, \cite{gregg2009temporal} studies spatial distribution of gas emission at the US-state level. The geography of fuel prices also have important implications on effective costs, as shows \cite{combes2005transport} by determining accurate transportation costs across urban areas for France. More closely related to our work, and using very similar daily open data for France, \cite{gautier2015dynamics} investigate dynamics of transmission from crude oil prices to fuel retail prices. However, they do not introduce an explicit spatial model of prices diffusion and do not study spatio-temporal dynamics.

In this paper we adopt a different approach by proceeding to exploratory spatial analysis on US fuel prices. We show that most of the variation occurs between counties and not across time, although crude oil price was not constant during the period considered. We therefore turn to a spatial analysis of the distribution of fuel prices. Our main findings are twofold: first we show that there are significant spatial pattern in some large US regions, second we show that even if most of the observed variation can be explained by state level policies, and especially the level of tax, some county level characteristics are still significant.

@@

The availability of new type of data has induced consequent changes in various disciplines from social science (e.g. online social network analysis~(\cite{tan2013social})) to geography (e.g. new insights into urban mobility or perspectives on ``smarter'' cities~(\cite{batty2013big})) including economics where the availability of exhaustive individual or firm level data is seen as a revolution of the field. Most studies involving these new data are at the interface of implied disciplines, what is both an advantage but also a source of difficulties. For example misunderstandings between physics and urban sciences described in \cite{dupuy2015sciences} are in particular caused by different attitudes towards unconventional data or divergent interpretations and ontologies of it. Collection and use of new data has therefore become a crucial stack in social-science. The construction of such datasets is however far from straightforward because of the incomplete and noisy nature of data. Specific technical tools have to be implemented but have often been designed to overcome one specific problem and are difficult to generalize. We develop such a tool that fills the following constraints that are typical of large scale data collection: (i) reasonable level of flexibility and generality; (ii) optimized performance through parallel collection jobs; (iii) anonymity of collection jobs to avoid any possible bias in the behavior of the data source. The architecture, at a high level, has the following structure:
\begin{itemize}
\item An independent pool of tasks runs continuously socket proxies to pipe requests through \texttt{tor}.
\item A manager monitors current collection tasks, split collection between subtasks and launches new ones when necessary.
\item Subtasks can be any callable application taken as argument destination urls, they proceed to the crawling, parsing and storage of collected data.
\end{itemize}
The application is open and its modules are reusable: source code is available on the repository of the project.\footnote{at \texttt{https://github.com/JusteRaimbault/EnergyPrice}} We constructed our dataset by using the tool continuously in time during two months to collect crowdsourced data available from various online sources.

@@

Our dataset comprises around $41\cdot 10^6$ unique observations of retail fuel prices at the station level, spanning the period starting the $10^{th}$ of January 2017 and ending the $19^{th}$ of March 2017 and corresponds to 118,573 unique retail stations. For each of these stations, we associate a precise geographical location (city resolution). On average we have 377 price information by station. Prices correspond to a unique purchase mode (credit card, other modes such as cash being less than 10\% in test datasets, they were discarded in the final dataset) and four possible fuel types: Diesel (18\% of observations), Regular (34\%), Midgrade (24\%) and Premium (24\%). The best coverage of stations is for Regular fuel type with on average 4,629 price information by county. We therefore choose to focus the study to this type of fuel, keeping in mind that further developments with the dataset may include comparative analysis on fuel types.
Our final dataset thus contains 14,192,352 observations from 117,155 gas station, followed during 68 days. We further aggregate these data by day, taking the average of the observed price per gallon, to obtain a panel of 5,204,398 gas station - day observations.\footnote{The panel is not balanced as prices are not reported every day in every station. The average gas station has information on price for 44 days (over 68).}  Table \ref{tab:stat_desc} gives some basic descriptive statistics of on price data showing that the distribution of oil price is highly concentrated with a small skewness (the ratio of the $99^{th}$ to the $1^{st}$ percentile is 1.6). 
Finally, in the spatial analysis, we will also use socio-economic data at the county level, available from the US Census Bureau. We shall use the latest available, what most of the time implies relying to the 2010 Census.

@@

Before moving to a more systematic study of the variation of fuel price, we propose a first exploratory introduction to give insight about its spatio-temporal structure. This exercise is a crucial stage to guide further analyses, but also to understand their implications in a geographical context. To explore the data, we built a simple web application which allow to map the data in space and time. This application is available on \href{http://shiny.parisgeo.cnrs.fr/fuelprice/}{this page}. We also show one example of mapping the data at the county level in Figure \ref{fig:map_price} where we used average price over the whole period. We clearly see regional patterns with the Southcentral and Southeast regions having the lowest prices and the Pacific cost and Northeast the highest prices. Of course, plotting aggregated data over the whole period does not bring much information about the time variation of the data. As we will show more in detail below most of the variation of fuel price occurs across space. A variance decomposition of fuel price yields only 11\% of the total variance is explained by within gas station variations. Similarly, the Spearman's rank correlation coefficient between the gas station price of regular fuel in the first day of dataset and in the last day is 0.867, and the null hypothesis that these two information are independent is strongly rejected.

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\textwidth]{average_regular_map}
\caption{Map of mean price for counties, regular fuel, averaged over the whole period.}\vspace{-0.3cm}
\label{fig:map_price}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{moran_days}
\includegraphics[width=0.48\textwidth]{moran_decay_weeks}
\caption{\textbf{Behavior of Moran spatial-autocorrelation index.} (Left) Evolution in time of Moran index computed on daily time windows, for different decay parameter values. (Right) Moran index as a function of decay parameter, computed on weekly time windows.}
\label{fig:moran}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{gwr_allbest_betaincome}
\includegraphics[width=0.48\textwidth]{gwr_allbest_betapercapjobs}\\
%\includegraphics[width=0.48\textwidth]{figures/gwr_allbest_residual}
\includegraphics[width=0.48\textwidth]{gwr_allbest_wage}
\includegraphics[width=0.48\textwidth]{gwr_allbest_LocalR2}
\caption{\textbf{Results of GWR analyses.} For the best model in the sense of AICc, we map the spatial distribution of fitted coefficient, in order from left to right and top to bottom, $\beta_{income}$, $\beta_{percapjobs}$, $\beta_{wage}$, and finally the local r-squared values.}
\label{fig:gwr}
\end{figure}

@@

Since our initial database enables to look at the level of variable $x_{i,s,c,t}$, the fuel price in day $t$, in gas station $i$, in state $s$ and in county $c$, we start by running high dimensional fixed effect regressions following the model:
\begin{eqnarray}
x_{i,s,c,t} &=& \beta_s + \varepsilon_{i,s,c,t} \\
x_{i,s,c,t} &=& \beta_c + \varepsilon_{i,s,c,t} \\
x_{i,s,c,t} &=& \beta_i + \varepsilon_{i,s,c,t}\\
\end{eqnarray}

Where $\varepsilon_{i,s,c,t}$ contains an idiosyncratic error and a day fixed effect. This first analysis confirm that most of the variance can be explained by a state fixed effect and that integrating more accurate levels has only small effect on the fit of our model as measured by the R-squared.

@@

One important aspect of our contribution is methodological. We show that to explore a new panel dataset, geographers and economists have different approach, leading to similar generic conclusions but with different paths. Some studies have already combined GWR and multi-level regressions (\cite{chen2012using}), or compared them in terms of model fit or robustness (\cite{lee2009determinants}). We take here a multi-disciplinary point of view and combines approaches answering to different questions, GWR aiming at finding precise explicative variables and to measure the extent of spatial correlation, whereas econometric models explain with more accuracy the effect of factors at different levels (state, county) but take these geographical characteristics as exogenous. We claim that both are necessary to understand all dimensions of the studied phenomenon.

@@

Another application of such analysis is to help better designing car-regulation policies. Environmental and health issues nowadays require a reasoned use of cars, in cities with the problem air pollution but also overall to reduce carbon emissions. \cite{fullerton2002can} showed that a taxation of fuel and cars can be equivalent to a taxation on emissions. \cite{brand2013accelerating} highlight the role of incentives for the transition towards a low carbon transportation. However, such measures can't be uniform across states or even counties for obvious reasons of territorial equity: areas with different socio-economic characteristics or with different amenities shall contribute regarding their capabilities and preferences. Knowing local prices dynamics and their drivers, in which our study is a preliminary step, may be a path to localized policies taking into account the socio-economic configuration and include an equity criterion.

@@

We have described a first exploratory study of US fuel prices in space and time, using a new database at the gas station level spanning two months. Our first result is to show the high spatial heterogeneity of price processes, using interactive data exploration and auto-correlation analyses. We proceed with two complementary studies of potential drivers: GWR unveils spatial structures and geographical particularities, and yields a characteristic scale of processes around 75km; multi-level regressions show that even though most of the variation can be explained by state level characteristics, and mostly by the level of the tax on fuel that is set by the state, there are still socio-economic specificities at the county level that can explain spatial variation of fuel price.

@@

%The citation must be used in following style: \cite{article-minimal} \cite{article-full} \cite{article-crossref} \cite{whole-journal}.
%% References with BibT

\begin{thebibliography}{15}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\providecommand{\url}[1]{\texttt{#1}}
\providecommand{\href}[2]{#2}
\providecommand{\path}[1]{#1}
\providecommand{\DOIprefix}{doi:}
\providecommand{\ArXivprefix}{arXiv:}
\providecommand{\URLprefix}{URL: }
\providecommand{\Pubmedprefix}{pmid:}
\providecommand{\doi}[1]{\href{http://dx.doi.org/#1}{\path{#1}}}
\providecommand{\Pubmed}[1]{\href{pmid:#1}{\path{#1}}}
\providecommand{\bibinfo}[2]{#2}
\ifx\xfnm\relax \def\xfnm[#1]{\unskip,\space#1}\fi
%Type = Article
\bibitem[{Batty(2013)}]{batty2013big}
\bibinfo{author}{Batty, M.}, \bibinfo{year}{2013}.
\newblock \bibinfo{title}{Big data, smart cities and city planning}.
\newblock \bibinfo{journal}{Dialogues in Human Geography} \bibinfo{volume}{3},
  \bibinfo{pages}{274--279}.
%Type = Article
\bibitem[{Brand et~al.(2013)Brand, Anable and Tran}]{brand2013accelerating}
\bibinfo{author}{Brand, C.}, \bibinfo{author}{Anable, J.},
  \bibinfo{author}{Tran, M.}, \bibinfo{year}{2013}.
\newblock \bibinfo{title}{Accelerating the transformation to a low carbon
  passenger transport system: The role of car purchase taxes, feebates, road
  taxes and scrappage incentives in the uk}.
\newblock \bibinfo{journal}{Transportation Research Part A: Policy and
  Practice} \bibinfo{volume}{49}, \bibinfo{pages}{132--148}.
%Type = Article
\bibitem[{Brunsdon et~al.(1996)Brunsdon, Fotheringham and
  Charlton}]{brunsdon1996geographically}
\bibinfo{author}{Brunsdon, C.}, \bibinfo{author}{Fotheringham, A.S.},
  \bibinfo{author}{Charlton, M.E.}, \bibinfo{year}{1996}.
\newblock \bibinfo{title}{Geographically weighted regression: a method for
  exploring spatial nonstationarity}.
\newblock \bibinfo{journal}{Geographical analysis} \bibinfo{volume}{28},
  \bibinfo{pages}{281--298}.
%Type = Article
\bibitem[{Chen and Truong(2012)}]{chen2012using}
\bibinfo{author}{Chen, D.R.}, \bibinfo{author}{Truong, K.},
  \bibinfo{year}{2012}.
\newblock \bibinfo{title}{Using multilevel modeling and geographically weighted
  regression to identify spatial variations in the relationship between
  place-level disadvantages and obesity in taiwan}.
\newblock \bibinfo{journal}{Applied Geography} \bibinfo{volume}{32},
  \bibinfo{pages}{737--745}.
%Type = Article
\bibitem[{Combes and Lafourcade(2005)}]{combes2005transport}
\bibinfo{author}{Combes, P.P.}, \bibinfo{author}{Lafourcade, M.},
  \bibinfo{year}{2005}.
\newblock \bibinfo{title}{Transport costs: measures, determinants, and regional
  policy implications for france}.
\newblock \bibinfo{journal}{Journal of Economic Geography} \bibinfo{volume}{5},
  \bibinfo{pages}{319--349}.
%Type = Article
\bibitem[{Dupuy and Benguigui(2015)}]{dupuy2015sciences}
\bibinfo{author}{Dupuy, G.}, \bibinfo{author}{Benguigui, L.G.},
  \bibinfo{year}{2015}.
\newblock \bibinfo{title}{Sciences urbaines: interdisciplinarit{\'e}s passive,
  na{\"\i}ve, transitive, offensive}.
\newblock \bibinfo{journal}{M{\'e}tropoles} .
%Type = Article
\bibitem[{Fullerton and West(2002)}]{fullerton2002can}
\bibinfo{author}{Fullerton, D.}, \bibinfo{author}{West, S.E.},
  \bibinfo{year}{2002}.
\newblock \bibinfo{title}{Can taxes on cars and on gasoline mimic an
  unavailable tax on emissions?}
\newblock \bibinfo{journal}{Journal of Environmental Economics and Management}
  \bibinfo{volume}{43}, \bibinfo{pages}{135--157}.
%Type = Article
\bibitem[{Gautier and Saout(2015)}]{gautier2015dynamics}
\bibinfo{author}{Gautier, E.}, \bibinfo{author}{Saout, R.L.},
  \bibinfo{year}{2015}.
\newblock \bibinfo{title}{The dynamics of gasoline prices: Evidence from daily
  french micro data}.
\newblock \bibinfo{journal}{Journal of Money, Credit and Banking}
  \bibinfo{volume}{47}, \bibinfo{pages}{1063--1089}.
%Type = Article
\bibitem[{Gregg et~al.(2009)Gregg, Losey, Andres, Blasing and
  Marland}]{gregg2009temporal}
\bibinfo{author}{Gregg, J.S.}, \bibinfo{author}{Losey, L.M.},
  \bibinfo{author}{Andres, R.J.}, \bibinfo{author}{Blasing, T.},
  \bibinfo{author}{Marland, G.}, \bibinfo{year}{2009}.
\newblock \bibinfo{title}{The temporal and spatial distribution of carbon
  dioxide emissions from fossil-fuel use in north america}.
\newblock \bibinfo{journal}{Journal of Applied Meteorology and Climatology}
  \bibinfo{volume}{48}, \bibinfo{pages}{2528--2542}.
%Type = Inproceedings
\bibitem[{Lee et~al.(2009)Lee, Kang and Kim}]{lee2009determinants}
\bibinfo{author}{Lee, S.}, \bibinfo{author}{Kang, D.}, \bibinfo{author}{Kim,
  M.}, \bibinfo{year}{2009}.
\newblock \bibinfo{title}{Determinants of crime incidence in korea: a mixed gwr
  approach}, in: \bibinfo{booktitle}{World conference of the spatial
  econometrics association}, pp. \bibinfo{pages}{8--10}.
%Type = Article
\bibitem[{Macharis et~al.(2010)Macharis, Van~Hoeck, Pekin and
  Van~Lier}]{macharis2010decision}
\bibinfo{author}{Macharis, C.}, \bibinfo{author}{Van~Hoeck, E.},
  \bibinfo{author}{Pekin, E.}, \bibinfo{author}{Van~Lier, T.},
  \bibinfo{year}{2010}.
\newblock \bibinfo{title}{A decision analysis framework for intermodal
  transport: Comparing fuel price increases and the internalisation of external
  costs}.
\newblock \bibinfo{journal}{Transportation Research Part A: Policy and
  Practice} \bibinfo{volume}{44}, \bibinfo{pages}{550--561}.
%Type = Article
\bibitem[{Rietveld et~al.(2001)Rietveld, Bruinsma and
  Van~Vuuren}]{rietveld2001spatial}
\bibinfo{author}{Rietveld, P.}, \bibinfo{author}{Bruinsma, F.},
  \bibinfo{author}{Van~Vuuren, D.}, \bibinfo{year}{2001}.
\newblock \bibinfo{title}{Spatial graduation of fuel taxes; consequences for
  cross-border and domestic fuelling}.
\newblock \bibinfo{journal}{Transportation Research Part A: Policy and
  Practice} \bibinfo{volume}{35}, \bibinfo{pages}{433--457}.
%Type = Article
\bibitem[{Rietveld and van Woudenberg(2005)}]{rietveld2005fuel}
\bibinfo{author}{Rietveld, P.}, \bibinfo{author}{van Woudenberg, S.},
  \bibinfo{year}{2005}.
\newblock \bibinfo{title}{Why fuel prices differ}.
\newblock \bibinfo{journal}{Energy Economics} \bibinfo{volume}{27},
  \bibinfo{pages}{79--92}.
%Type = Article
\bibitem[{Tan et~al.(2013)Tan, Blake, Saleh and Dustdar}]{tan2013social}
\bibinfo{author}{Tan, W.}, \bibinfo{author}{Blake, M.B.},
  \bibinfo{author}{Saleh, I.}, \bibinfo{author}{Dustdar, S.},
  \bibinfo{year}{2013}.
\newblock \bibinfo{title}{Social-network-sourced big data analytics}.
\newblock \bibinfo{journal}{IEEE Internet Computing} \bibinfo{volume}{17},
  \bibinfo{pages}{62--69}.
%Type = Article
\bibitem[{Tsai(2005)}]{tsai2005quantifying}
\bibinfo{author}{Tsai, Y.H.}, \bibinfo{year}{2005}.
\newblock \bibinfo{title}{Quantifying urban form: compactness versus' sprawl'}.
\newblock \bibinfo{journal}{Urban studies} \bibinfo{volume}{42},
  \bibinfo{pages}{141--161}.

\end{thebibliography}
%eX database:

%\bibliographystyle{elsarticle-harv}
%\bibliography{biblio}
%
